### 2015-03-15 article/article.tex
commit

	C57L/J & Esr2 (estrogen receptor 2 beta) & 
	relative size of perivascular immune cell clusters &  3.5\\
	CE/J & Rorb (RAR-related orphan receptor beta) & 
	tigloylglycine (16h fast), relative abundance&  3.3\\
	NOD/\\ShiLtJ & Ppard (peroxisome proliferator activator receptor delta) & 
	percentage of parasites in brain relative to all organs tested &  3.1\\ 

@@

@@

Moreover, Figures~\ref{fig:mpi_pheotypes_strain_zscore2} and~\ref{fig:mpi_pheotypes_strain_zscore2_neg} provide an insight into the exact association of each phenotype with the corresponding nuclear receptor genes. Therefore, there are ... genes associated with the extreme high phenotypes and 5 genes associated with the extreme low phenotypes, respectively, as following: \textit{Rora}, \textit{Esr1}, \textit{Esrrg}, \textit{Thrb} and \textit{Nr3c2}. 

>>>>

	C57L/J & Esr2 (estrogen receptor 2 beta) & relative size of perivascular immune cell clusters &  3.5\\
	CE/J & Rorb (RAR-related orphan receptor beta) & tigloylglycine (16h fast), relative abundance&  3.3\\
	NOD/\\ShiLtJ & Ppard (peroxisome proliferator activator receptor delta) & percentage of parasites in brain relative to all organs tested &  3.1\\ 

@@

	tdb & Esrrg ( ... ) & tbd &  tbd\\ 

@@

Moreover, Figures~\ref{fig:mpi_pheotypes_strain_zscore2} and~\ref{fig:mpi_pheotypes_strain_zscore2_neg} provide an insight into the exact association of each phenotype with the corresponding nuclear receptor genes. Therefore, there are 4 genes associated with the extreme high and low phenotypes respectively, as following: \textit{Rora - RAR-related orphan receptor alpha}, \textit{Esr1 - estrogen receptor 1 alpha}, \textit{Esrrg - estrogen-related receptor gamma}, \textit{Thrb - thyroid hormone receptor, beta} and a fifth gene associated only with extreme low phenotypes - \textit{Nr3c2}. 
